Physics-Informed Neural ODEs (PINODE)

### 2023-05-17 presentation/phd_defense_pres.tex
Add slides for physics-informed loss

\begin{frame}{Physics-Informed Loss}
1) We introduce physics to this system by adding a term which regularises latent gradient field. 
2) In particular, it forces it to be equal to what a true physics should be under such projection.
3) We can not evaluate physics everywhere but we can at particular carefully-selected points. We call these points collocation points.
4) We feed a lot of collocation points and ask a network to do interpolation \end{frame}

@@

\begin{frame}{Results: Burger's Equation}
	Results on Burgers
	Maybe results on a harder problem
\end{frame}

\begin{frame}{Results: Kolmogorov Flow OR Real Example}

@@

>>>>

\begin{frame}{Physics-Informed Loss}
%1) We introduce physics to this system by adding a term which regularizes latent gradient field. 
%2) In particular, it forces it to be equal to what a true physics should be under such projection.
%3) We can not evaluate physics everywhere but we can at particular carefully-selected points. We call these points collocation points.
%4) We feed a lot of collocation points and ask a network to do interpolation 
\includegraphics[width=\textwidth]{Figures/collocations_1.png}
\end{frame}

\begin{frame}{Physics-Informed Loss}
	\includegraphics[width=\textwidth]{Figures/collocations_2.png}
\end{frame}

\begin{frame}{Physics-Informed Loss}
	\includegraphics[width=\textwidth]{Figures/collocations_3.png}
\end{frame}

\begin{frame}{Physics-Informed Loss}
	\includegraphics[width=\textwidth]{Figures/collocations_4.png}
\end{frame}

\begin{frame}{Physics-Informed Loss}
	\includegraphics[width=\textwidth]{Figures/collocations_5.png}
\end{frame}

@@

\begin{frame}{Results: Burger's Equation}
	When we capture 32 samples per frame:
	\includegraphics[width=\textwidth]{Figures/cs_burgers_comparison_32.pdf}
\end{frame}

\begin{frame}{Results: Burger's Equation}
	When we capture 32 samples per frame:
	\includegraphics[width=\textwidth]{Figures/cs_burgers_comparison_32.pdf}

	When we capture 2 samples per frame:
	\includegraphics[width=\textwidth]{Figures/cs_burgers_comparison_2.pdf}
\end{frame}

\begin{frame}{Results: Burger's Equation}
	Aggregated results
\end{frame}

\begin{frame}{Results: Interpretation}

@@

\begin{frame}{Results: Kolmogorov Flow OR Real Example}
\end{frame}
